Master thesis

### 2017-06-02 03-Model.Rmd
Model and M&M reorganized + sylviculture model v1

```{r traits, echo=FALSE}
table <- data.frame(
  Abbreviation = c('$LMA$', '$N_m$', '$P_m$', '$wsg$', '$dbh_{thresh}$', '$h_{lim}$', '$a_h$'),
  Description = c('leaf mass per area', 'leaf nitrogen content per dry mass', 'leaf phosphorous content per dry mass', 'wood specific gravity', 'diameter at breasth height threshold', 'asymptotic height', 'parameter of the tree-height-dbh allometry'),
  Units = c('$g.m^-2$', '$mg.g^-1$', '$mg.g^-1$', '$g.cm^-3$', '$m$', '$m$', '$m$')
)
knitr::kable(table, caption = 'Species-specific parameters used in TROLL from @Li. Data originates from the BRIDGE [@Baraloto2010] and TRY [@Kattge2011] datasets.')
```

Carbon assimilation is computed over half-hourly period of a representative day. Then allocation is computed to simulate tree growth from an explicit carbone balance (in contrast to previous models). Finally environment is updated at each timestep set to one month. Seedlings are not simulated explicitly but as a pool. In addition belowground processes, herbaceous plants, epiphytes and lianas are not simulated inside TROLL. The source code is written in C++ and available upon request. All analyses were conducted in R version 3.4.0 **Cite R, add entry in Mendeley**.

@@

## Abiotic environment

A voxel space, with a resolution of 1 $m^3$, is used to explicilty model the abiotic environment. For each tree crown, leaf area density is calculated on tree geometry assuming a uniform distriution across voxels occupied by the crown. Leaf area density is computed within each voxel summing all tree crowns inside the voxel $v$, and is denoted $LAD(v)$ (leaf area per voxel in $m².m^-3$). The vertical sum of $LAD$ from voxel $v$ to the ground level defines $LAI(v)$ (leaf area per fround area in $m^2.m^-2$ commonly called leaf area index):

\begin{equation}
  LAI(v) = \sum _{v'=v} ^\infty LAD(v') 
  (\#eq:LAI)
\end{equation}

Daily variations in light intensity (photosynthetic photon flux density PPFD in $\mu mol_{photons}.m^-2.s^-1$), temperature (T in degrees Celsius), and vapor pressure deficit (VPD in $kPA$) are computed to assess carbon assimilation within each voxel of the canopy and for a representative day per month (see Appendix 1 from @Li for further details). Variation of PPFD Within the canopy is calculated as a loacal Beer-Lambert extinction law:

\begin{equation}
  PPFD_{max,month}(v) = PPFD_{top,max,month}*e^{-k*LAI(v)}
  (\#eq:PPFD)
\end{equation}

The daily maximum incident PPFD at the top of canopy $PPFD_{top,max,month}$ is given as input. The extinction rate $k$ is assumed as constant (see table \@ref(tab:par) for parameters value), besides is variation with zenith angle and species leaf inclination angle [@Meir2000]. Moreover only vertical light diffusion is considered ignoring lateral light diffusion, which can have an important role especially in logging gaps. Finally, intra-day variation at half hour time steps $t$ for a representative day every month are used to compute $PPFD_{month}(v,t)$, $T_{month}(v,t)$ and $VPD_{month}(v,t)$. Water and nutrient process both in soil and inside trees are not simulated.

## Photosynthesis

## Autotrophic respiration

## Carbon uptake

## Tree growth

## Recruitment

## Mortality

>>>>

@@

Carbon assimilation is computed over half-hourly period of a representative day. Then allocation is computed to simulate tree growth from an explicit carbone balance (in contrast to previous models). Finally environment is updated at each timestep set to one month. Seedlings are not simulated explicitly but as a pool. In addition belowground processes, herbaceous plants, epiphytes and lianas are not simulated inside TROLL. The source code is written in C++ and available upon request. All modules of TROLL models are further detailed in [Appendix 1].

```{r traits, echo=FALSE}
table <- data.frame(
  Abbreviation = c('$LMA$', '$N_m$', '$P_m$', '$wsg$', '$dbh_{thresh}$', '$h_{lim}$', '$a_h$'),
  Description = c('leaf mass per area', 'leaf nitrogen content per dry mass', 'leaf phosphorous content per dry mass', 'wood specific gravity', 'diameter at breasth height threshold', 'asymptotic height', 'parameter of the tree-height-dbh allometry'),
  Units = c('$g.m^{-2}$', '$mg.g^{-1}$', '$mg.g^{-1}$', '$g.cm^{-3}$', '$m$', '$m$', '$m$')
)
knitr::kable(table, caption = 'Species-specific parameters used in TROLL from @Li. Data originates from the BRIDGE [@Baraloto2010] and TRY [@Kattge2011] datasets.', format = 'pandoc')
```

Previous implementation of TROLL model used @Reich1991a allometry to infer leaf lifespan $LL$ from species leaf mass per area $LMA$ [@Li, see [Appendix 1]]. But the use of the allometrie from @Reich1991a with current implementation of the TROLL model resulted in an underestimation of leaf lifespan for low LMA species. Consequently in the following paragraph we suggest a new allometry.

Selective logging is defined as the targeted harvesting of timber from species of interest. Consequently, tropical sylviculture can be assimilated to a disturbance. The main difference between a disturbance and selective logging is the targetting of both species and individuals of interest. So we decided to first asses unselective disturbance effect on tropical forest ecosystem to subsequently better understand selective logging effect. First, we implemented a disturbance module inside TROLL model to simulate unselective disturbance. Secondly, we implemented a sylviculture module inside TROLL model to simulate selective logging in regards to french Guiana practices.

## Leaf lifespan

The underestimation of leaf lifespan for low LMA species with the allometry from @Reich1991a resulted in indivduals unealistic early death from carbon starvation. We gathered data from TRY[@Kattge2011], DRYAD [@chave_towards_2009] and GLOPNET [@wright_worldwide_2004] datasets. We used an out of the bag method applied on a random forest to select variables with highest importance to explain leaf lifespan. We thus selected leaf mass per are $LMA$, leaf nitrogen content $N$ and wood specific gravity $wsg$. We then used a bayesian approach to test different models with growing level of complexity. The model with the best tradeoff between complexity (number of parameters), convergence, likelihood, and prediction quality (root mean square error of prediction RMSEP) was kept. We selected following model with a maximum likelihood of 13.6 and a RMSEP of 12 months:

\begin{equation}
  LL_{d} \sim log\mathcal{N}({\beta_1}_d*LMA - {\beta_2}_d*N*\beta_3*wsg, \sigma)
  (\#eq:LL)
\end{equation}

Leaf lifespan $LL$ follows a lognormal law with location infered from leaf lifespan $LMA$, nitrogen content $N$ and wood specific gravity $wsg$ and a scale $\sigma$. Each ${\beta_i}_d$ is following a normal law located on $\beta_i$ with a scale of $\sigma_i$. All $\beta_i$, $\sigma_i$, and $\sigma$ are assumed without presemption following a gamma law. $d$ represents the dataset random effects and encompass environmental and protocol variations. **Add Appendix ?**

## Disturbance

Disturbance module was designed in the simplest way in order to relate the ecosystem answer to volume lost without any individuals nor species targetting. For a given iteration $disturb_{iter}$, individuals are picked randomly with a uniform law on the number of trees. Selected individuals are then removed without trigerring a treefall to avoid any side effect. The operation is repeated untill the disturbance result in a defined lost basal area ($disturb_{intensity}$ in % of BA).

## Sylviculture

In french guiana context sylviculture can be narrow to selective logging, which can be split in two steps: selection and harvesting. Selection encompass choice of the havrestable area, tree designation by the forest office, tree selection by the harvester, and removal off tree probbed as rotten by the lumber. Harvesting encompass tree felling, tracks opening, and long term damages (simplified in gap damages in current TROLL implementation).

### Designation and selection

One major limit of current implementation of TROLL model is that it assumes a flat environment. Consequently the whole simulated area inside TROLL is considered has an harvestable zone. With all commercial species minimum and maximum harvestable diameter, TROLL calculates the total harvestable volume ${V_h}_{tot}$. If the total harvestable volume ${V_h}_{tot}$ exceed $30~m^3.hectare^{-1}$, commercial species minimum harvestable diameter $dbh_{min}$ is increased untill ${V_h}_{tot}$ is inferior to that upper limit.

In french guiana, tree harvesters are focusing on few species with easier marketable wood, resulting in a tree harvest around $20~m^3.ha^{-1}$ (Laurent Descroix, ONF, personnal communication). TROLL ranks each commercial species on its economic value, and randomly remove individuals from lowest rank species untill it reaches total harvested volume ${V_{hd}}_{tot}$ (${V_{hd}}_{tot}$ was set to $25~m^3.hectare^{-1}$ in subsequent simulations).

### Rotten trees

20 to 30 % of designated trees are considered as rotten once probed by the lumberman.
Rotten trees are not random and depends both on tree species and diameter.

**Explain rotten bayesian model**

\begin{equation}
  P_{rotten} = logit^{-1}(\beta_0 + \beta_1*dbh) = \frac{e^{\beta_0 + \beta_1*dbh}}{1 + e^{\beta_0 + \beta_1*dbh}}
  (\#eq:rotten)
\end{equation}

**Add Appendix ?**

### Harvesting

Due to crown aspects, treefall from logs are often random (whereas difficult to manage, treefall can still be oriented, Laurent Descroix, ONF, personnal communication). Consequently, TROLL consider treefall from log as random like current natural treefall implementation inside TROLL (see code [Appendix 1]).

Tree harvesting roads are split in three classes: truck roads, main tractor track, and secondary track. Because TROLL assumes a flat environment, the main track is opened starting from the middle of one side of the simulated forest and untill it reaches the center with a width of 6 meters. In most cases, secondary tracks are opened once trees have been designated and the geolocation taken at a maximum distance of 30 meters from designated trees (Laurent Descroix, ONF, personnal communication). To simulate secondary tracks, TROLL uses a loads map, measuring every trees at a distance of 30 meters for each pixel, and  a track proximity maps of the closest existing track. Next, the model select the pixel with the highest load and closest track, find the closest existing track and join it by removing tree in the way with a width of 5 meters. The operations are repeated untill no felt trees are left.

### Gap damages

Most of models account long term damages due to selective logging with a 10 years increased mortality [@Huth2004; @Khler2004; @Ruger2008]. We decided to model explicitly long term logging damages because of their localised nature through a gap damages model. We gathered data from Paracou dataset **Cite** in cenususes between 1988 and 1992 on Paracou harvested plots. Individuals were categorized between alive, dead, or recruited during the period. We measured each individual distance to the closest gap. We then used a bayesian approach to test the link between tree death in the four years following the log event and distance to the closest gap. We adapted the model from **Cite Herault** based on a disturbance index into.

\begin{equation}
  \begin{array}{c} 
    Death_i \sim \mathcal{B}(P(Death_i)) \\
    P(Death_i) = logit^{-1}(\theta + \beta*e^{\alpha*d_{gaps}}) = \frac{e^{\theta + \beta*e^{\alpha*d_{gaps}}}}{1 + e^{\theta + \beta*e^{\alpha*d_{gaps}}}}
  \end{array}
  (\#eq:death)
\end{equation}

$Death$ of a tree $i$ follows a $\mathcal{Bernoulli}$ law of probability $P(Death_i)$. The odds for a tree $i$ to die $O(Death_i)$ is calculated by the sum of the natural tree death odd $\theta$ and a perturbation index $\beta*e^{\alpha*d_{gaps}}$. The perturbation index depend on the distance $d_{gaps}$ of the tree $i$ to the closest logging gap. The probability for a tree $i$ to die $P(Death_i)$ is finally calculated by taking the inverse logit of the odd $logit^{-1}[O(Death_i)]$. **Add Appendix ?**

### 2017-06-02 04-MnMs.Rmd
Model and M&M reorganized + sylviculture model v1

```{r config5, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()) ; invisible(gc())
library(ggplot2)
library(ggrepel)
```

# Disturbance

Most tropical timber production originates from selective logging, the targeted harvesting of timber from species of interest. Consequently, tropical sylviculture can be assimilated to a disturbance. The main difference between a disturbance and selective logging is the targetting of both species and individuals of interest. So we decided to first asses unselective disturbance effect on tropical forest ecosystem to subsequently better understand selective logging effect.

@@

## Model description

Disturbance module was designed in the simplest way in order to relate the ecosystem answer to volume lost without any individuals nor species targetting. For a given iteration $disturb_{iter}$, individuals are picked randomly with a uniform law on the number of trees. Selected individuals are then removed without trigerring a treefall to avoid any side effect. The operation is repeated untill the disturbance result in a defined lost basal area ($disturb_{intensity}$ in % of BA).

>>>>

# Material and Methods

## Sensitivity analysis

@Li already assessed TROLL model sensitivity to several parameters ($k$ see \@ref(eq:PPFD), $\phi$ see \@ref(eq:LCP), $g1$ see \@ref(eq:gs), $f_{wood}$ see \@ref(eq:DeltaV), $f_{canopy}$ see \@ref(eq:DeltaLA) and $m$ see \@ref(eq:db)) which they assumed having a key role in model functioning.

On the other hand, we decided to use TROLL to study resistance and resilience of ecosystem face to disturbance, highlighting the role of biodiversit. Consequently we particulrarly needed to assess the importance of functional traits to further better control and evaluate functional diversities. We also needed to assess the sensitivity of TROLL model to the seed rain constant ($n_{ext}$, see \@ref(eq:next)) because we assume it is one of the main factor of tree recruitments after disturbance in simulations.

TROLL model currenty uses leaf mass per area ($LMA$ in $g.m^{-2}$), leaf nitrogen content per dry mass ($N_m$ in $mg.g^{-1}$), leaf phosphorus content per dry mass ($P_m$ in $mg.g^{-1}$), wood specific gravity ($wsg$ in $g.cm^{-3}$), diameter at breasth height threshold ($dbh_{thresh}$ in $m$), asymptotic height ($h_{lim}$ in $m$), and parameter of the tree-height-dbh allometry ($a_h$ in $m$). To assess the sensitivity of TROLL model to species functionnal traits, we performed a sensitivity analysis by fixing species trait values to their mean. Each trait was tested independently. We reduce to a common mean traits with a Perason's correlation value $r \geq 0.8$ ($h_{max}$ and $a_h$ with a correlation of $r=0.98$).

To assess the sensitivity of TROLL model to seed rain, we performed a sensitivity analysis by fixing simulations seed rain constant to 2, 20, 200 and 2000 seeds per hectare (default value being 200 seeds per hectare).

Simulations were conducted on Intel Xeon(R) with 32 CPUs of 2.00GHz and 188.9 GB of memory. We assumed maturity of the forest after 500 years of regeneration (Maréchaux & Chave) and computed simulation 100 years after a disturbance event with 40% loss of basal area. Due to computer limitations we did not run replicate (besides it should be necessary to reduce simulation stochasticity). To assess ecosystem outputs sensitivity to studied parameters, we compared it to 100 replicates of control simulations with all parameters set to default values. Ecosystem outputs outside of the range of the control replicates values are significantly influenced by the studied parameter.

## Disturbance

*Most tropical timber production originates from selective logging, the targeted harvesting of timber from species of interest. Consequently, tropical sylviculture can be assimilated to a disturbance. The main difference between a disturbance and selective logging is the targetting of both species and individuals of interest. So we decided to first asses unselective disturbance effect on tropical forest ecosystem to subsequently better understand selective logging effect. We first implemented a simple disturbance module inside TROLL model to simulate unselective disturbance.* **Already inside model descripiton !**

@@

## Selective logging

Once the unselective effect of disturbance on forest ecosystem studied, we can focus on selective logging to highlight the effect of species and individuals targetting on the ecosystem answer. We first implemented a sylviculture module inside TROLL model to simulate selective logging in regards to french Guiana practices. We used the 60 communities from disturbance simulations to study the role of biodiversity in both forest ecosystem and commercial species answer to selective logging. We then

### 2017-06-02 docs/master-thesis.tex
template.tex v3 (geometry, fontsize, baselinestretch)
Model and M&M reorganized + sylviculture model v1

%%% STYLE %%%
\documentclass[]{article}

@@

@@

@@

@@

Carbon assimilation is computed over half-hourly period of a
representative day. Then allocation is computed to simulate tree growth
from an explicit carbone balance (in contrast to previous models).
Finally environment is updated at each timestep set to one month.
Seedlings are not simulated explicitly but as a pool. In addition
belowground processes, herbaceous plants, epiphytes and lianas are not
simulated inside TROLL. The source code is written in C++ and available
upon request. All analyses were conducted in R version 3.4.0
\textbf{Cite R, add entry in Mendeley}.

@@

\(\tau_{young}\), \(\tau_{mature}\), and \(\tau_{old}\) are species
residence times in each leaf pools (\(years\)). The sum of residency
time thus defined the leaf lifespan
\(LL = \tau_{young} + \tau_{mature} + \tau_{old}\) (\(years\)).
\(\tau_{young}\) is set to one month and \(\tau_{mature}\) is set to a
third of leaf lifespan \(LL\). Previous implementation of TROLL model
used \citet{Reich1991a} allometry to infer leaf lifespan \(LL\) from
species leaf mass per area \(LMA\) \citep{Li}. But the use of the
allometrie from \citet{Reich1991a} with current implementation of the
TROLL model resulted in an underestimation of leaf lifespan for low LMA
species. Consequently in the following paragraph we suggest a new
allometry. Belowground carbon allocation is not simulated inside TROLL.

@@

\section{Sensitivity analysis}\label{sensitivity-analysis}

\subsection{Functional traits}\label{functional-traits}

\subsection{Seed rain}\label{seed-rain}

\section{Disturbance}\label{disturbance}

Most tropical timber production originates from selective logging, the
targeted harvesting of timber from species of interest. Consequently,
tropical sylviculture can be assimilated to a disturbance. The main
difference between a disturbance and selective logging is the targetting
of both species and individuals of interest. So we decided to first
asses unselective disturbance effect on tropical forest ecosystem to
subsequently better understand selective logging effect.

\subsection{Model description}\label{model-description-1}

\section{Selective logging}\label{selective-logging}

Once the unselective effect of disturbance on forest ecosystem studied,
we can focus on selective logging to highlight the effect of species and
individuals targetting on the ecosystem answer.

\subsection{Model description}\label{model-description-2}

\subsubsection{Designation}\label{designation}

\subsubsection{Selection}\label{selection}

\subsubsection{Felling}\label{felling}

\subsubsection{Tracks}\label{tracks}

\subsection{Design of experiment}\label{design-of-experiment-1}

\subsection{Ecosystem answer
anlaysis}\label{ecosystem-answer-anlaysis-1}

Similar to disturbance

\bibliography{/home/sylvain/Documents/Bibliography/library.bib}
\listoftables
\listoffigures

>>>>

%%% STYLE %%%
\documentclass[12pt,]{article}

@@

% geometry
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\renewcommand{\baselinestretch}{1.1}

@@

\begin{itemize}
\tightlist
\item
  Bruno
\item
  Stéphane
\item
  Laurent
\item
  Fabian
\item
  Isabelle
\item
  Jérôme
\item
  Camilla
\item
  Aurélie
\item
  Éric
\item
  \ldots{}
\end{itemize}

@@

Carbon assimilation is computed over half-hourly period of a
representative day. Then allocation is computed to simulate tree growth
from an explicit carbone balance (in contrast to previous models).
Finally environment is updated at each timestep set to one month.
Seedlings are not simulated explicitly but as a pool. In addition
belowground processes, herbaceous plants, epiphytes and lianas are not
simulated inside TROLL. The source code is written in C++ and available
upon request. All modules of TROLL models are further detailed in
\protect\hyperlink{appendix-1}{Appendix 1}.

@@

Previous implementation of TROLL model used \citet{Reich1991a} allometry
to infer leaf lifespan \(LL\) from species leaf mass per area \(LMA\)
\citep[see \protect\hyperlink{appendix-1}{Appendix 1}]{Li}. But the use
of the allometrie from \citet{Reich1991a} with current implementation of
the TROLL model resulted in an underestimation of leaf lifespan for low
LMA species. Consequently in the following paragraph we suggest a new
allometry.

Selective logging is defined as the targeted harvesting of timber from
species of interest. Consequently, tropical sylviculture can be
assimilated to a disturbance. The main difference between a disturbance
and selective logging is the targetting of both species and individuals
of interest. So we decided to first asses unselective disturbance effect
on tropical forest ecosystem to subsequently better understand selective
logging effect. First, we implemented a disturbance module inside TROLL
model to simulate unselective disturbance. Secondly, we implemented a
sylviculture module inside TROLL model to simulate selective logging in
regards to french Guiana practices.

\begin{equation}
  LL_{d} \sim log\mathcal{N}({\beta_1}_d*LMA - {\beta_2}_d*N*\beta_3*wsg, \sigma)
  \label{eq:LL}
\end{equation}

Leaf lifespan \(LL\) follows a lognormal law with location infered from
leaf lifespan \(LMA\), nitrogen content \(N\) and wood specific gravity
\(wsg\) and a scale \(\sigma\). Each \({\beta_i}_d\) is following a
normal law located on \(\beta_i\) with a scale of \(\sigma_i\). All
\(\beta_i\), \(\sigma_i\), and \(\sigma\) are assumed without
presemption following a gamma law. \(d\) represents the dataset random
effects and encompass environmental and protocol variations. \textbf{Add
Appendix ?}

\subsection{Disturbance}\label{disturbance}

In french guiana context sylviculture can be narrow to selective
logging, which can be split in two steps: selection and harvesting.
Selection encompass choice of the havrestable area, tree designation by
the forest office, tree selection by the harvester, and removal off tree
probbed as rotten by the lumber. Harvesting encompass tree felling,
tracks opening, and long term damages (simplified in gap damages in
current TROLL implementation).

\subsubsection{Designation and
selection}\label{designation-and-selection}

One major limit of current implementation of TROLL model is that it
assumes a flat environment. Consequently the whole simulated area inside
TROLL is considered has an harvestable zone. With all commercial species
minimum and maximum harvestable diameter, TROLL calculates the total
harvestable volume \({V_h}_{tot}\). If the total harvestable volume
\({V_h}_{tot}\) exceed \(30~m^3.hectare^{-1}\), commercial species
minimum harvestable diameter \(dbh_{min}\) is increased untill
\({V_h}_{tot}\) is inferior to that upper limit.

In french guiana, tree harvesters are focusing on few species with
easier marketable wood, resulting in a tree harvest around
\(20~m^3.ha^{-1}\) (Laurent Descroix, ONF, personnal communication).
TROLL ranks each commercial species on its economic value, and randomly
remove individuals from lowest rank species untill it reaches total
harvested volume \({V_{hd}}_{tot}\) (\({V_{hd}}_{tot}\) was set to
\(25~m^3.hectare^{-1}\) in subsequent simulations).

20 to 30 \% of designated trees are considered as rotten once probed by
the lumberman. Rotten trees are not random and depends both on tree
species and diameter.

\textbf{Explain rotten bayesian model}

\begin{equation}
  P_{rotten} = logit^{-1}(\beta_0 + \beta_1*dbh) = \frac{e^{\beta_0 + \beta_1*dbh}}{1 + e^{\beta_0 + \beta_1*dbh}}
  \label{eq:rotten}
\end{equation}

\textbf{Add Appendix ?}

\subsubsection{Harvesting}\label{harvesting}

Due to crown aspects, treefall from logs are often random (whereas
difficult to manage, treefall can still be oriented, Laurent Descroix,
ONF, personnal communication). Consequently, TROLL consider treefall
from log as random like current natural treefall implementation inside
TROLL (see code \protect\hyperlink{appendix-1}{Appendix 1}).

Tree harvesting roads are split in three classes: truck roads, main
tractor track, and secondary track. Because TROLL assumes a flat
environment, the main track is opened starting from the middle of one
side of the simulated forest and untill it reaches the center with a
width of 6 meters. In most cases, secondary tracks are opened once trees
have been designated and the geolocation taken at a maximum distance of
30 meters from designated trees (Laurent Descroix, ONF, personnal
communication). To simulate secondary tracks, TROLL uses a loads map,
measuring every trees at a distance of 30 meters for each pixel, and a
track proximity maps of the closest existing track. Next, the model
select the pixel with the highest load and closest track, find the
closest existing track and join it by removing tree in the way with a
width of 5 meters. The operations are repeated untill no felt trees are
left.

Most of models account long term damages due to selective logging with a
10 years increased mortality \citep{Huth2004, Khler2004, Ruger2008}. We
decided to model explicitly long term logging damages because of their
localised nature through a gap damages model. We gathered data from
Paracou dataset \textbf{Cite} in cenususes between 1988 and 1992 on
Paracou harvested plots. Individuals were categorized between alive,
dead, or recruited during the period. We measured each individual
distance to the closest gap. We then used a bayesian approach to test
the link between tree death in the four years following the log event
and distance to the closest gap. We adapted the model from \textbf{Cite
Herault} based on a disturbance index into.

\begin{equation}
  \begin{array}{c} 
    Death_i \sim \mathcal{B}(P(Death_i)) \\
    P(Death_i) = logit^{-1}(\theta + \beta*e^{\alpha*d_{gaps}}) = \frac{e^{\theta + \beta*e^{\alpha*d_{gaps}}}}{1 + e^{\theta + \beta*e^{\alpha*d_{gaps}}}}
  \end{array}
  \label{eq:death}
\end{equation}

\(Death\) of a tree \(i\) follows a \(\mathcal{Bernoulli}\) law of
probability \(P(Death_i)\). The odds for a tree \(i\) to die
\(O(Death_i)\) is calculated by the sum of the natural tree death odd
\(\theta\) and a perturbation index \(\beta*e^{\alpha*d_{gaps}}\). The
perturbation index depend on the distance \(d_{gaps}\) of the tree \(i\)
to the closest logging gap. The probability for a tree \(i\) to die
\(P(Death_i)\) is finally calculated by taking the inverse logit of the
odd \(logit^{-1}[O(Death_i)]\). \textbf{Add Appendix ?}

\section{Material and Methods}\label{material-and-methods}

\subsection{Sensitivity analysis}\label{sensitivity-analysis}

\emph{Most tropical timber production originates from selective logging,
the targeted harvesting of timber from species of interest.
Consequently, tropical sylviculture can be assimilated to a disturbance.
The main difference between a disturbance and selective logging is the
targetting of both species and individuals of interest. So we decided to
first asses unselective disturbance effect on tropical forest ecosystem
to subsequently better understand selective logging effect. We first
implemented a simple disturbance module inside TROLL model to simulate
unselective disturbance.} \textbf{Already inside model descripiton !}

\subsection{Selective logging}\label{selective-logging}

Once the unselective effect of disturbance on forest ecosystem studied,
we can focus on selective logging to highlight the effect of species and
individuals targetting on the ecosystem answer. We first implemented a
sylviculture module inside TROLL model to simulate selective logging in
regards to french Guiana practices. We used the 60 communities from
disturbance simulations to study the role of biodiversity in both forest
ecosystem and commercial species answer to selective logging. We then

\subsection{Disturbance}\label{disturbance-2}

\subsection{Sylviculture}\label{sylviculture-1}

\appendix

\hypertarget{appendix-1}{\section{Appendix 1}\label{appendix-1}}

I this Appendix we further detail modules of TROLL model.

@@

\(\tau_{young}\), \(\tau_{mature}\), and \(\tau_{old}\) are species
residence times in each leaf pools (\(years\)). The sum of residency
time thus defined the leaf lifespan
\(LL = \tau_{young} + \tau_{mature} + \tau_{old}\) (\(years\)).
\(\tau_{young}\) is set to one month and \(\tau_{mature}\) is set to a
third of leaf lifespan \(LL\). Belowground carbon allocation is not
simulated inside TROLL.

\subsection{Leaf lifespan}\label{leaf-lifespan-1}

@@

\addcontentsline{toc}{section}{References}
\bibliography{/home/sylvain/Documents/Bibliography/library.bib}
\listoftables
\listoffigures
